Title here

### 2016-10-28 portfolio/text/ms.Rmd
Copy editing

We combined similar permits into permit groupings
and identified sets of
permit groupings held by an individual
in a specific year as 'strategies' (Supporting Information).
For example, we combined permits that were the same except for vessel size
(e.g. a longliner fishing sablefish on a vessel under 60 ft was
considered to have the same strategy as a longliner fishing
sablefish on a vessel over 60 ft),
and we combined a number of permits that were targeting a single species
and differed only in region fished.
Therefore, someone fishing herring roe in Kodiak
and someone fishing herring roe in Alaska Peninsula
were both considered to have a 'herring roe' permit group.
For salmon permits,
we grouped permits using the same gear type across regions
for groups that shared similar species composition.
After this process of combining permits,
we were left with `r n_grouped_permits`
unique fishing permit groups (Table S\ref{tab:strategies}),
which we aggregated
within each person-year combination
to form permit strategies.
For example, if someone fished halibut
and sablefish in the same year,
their strategy for that year would be `halibut-sablefish'.
Specific details on our strategy definitions are available in
the Supporting Information.

@@

\noindent
where $s$ indexes species from $1$ through $n$.
We calculated effort or effective season length as
the sum of the season lengths for each permit each year.
Season length for a given permit
was calculated as the the number of days between
the first instance of fishing a permit
and the last instance of fishing a permit each year.
For example, if someone fished for 30 days
on a salmon drift gillnet permit in Southeast Alaska
and 40 days on a statewide longline halibut permit,
that individual's season length
would be 70 days.

@@

To jointly model revenue and revenue variability as a function of
individual-level covariates, we use a variance function regression model, which
separately models change in the mean and variance as
a function of covariates [e.g. @davidian1987; @hall1989]. 
Whereas traditional linear models or 
hierarchical linear models generally assume
homoscedasticity --- that the residual variance 
is the same for all values of the predictor variables ---
the variance function regression model allows variance to be heteroskedastic. 
For application to economic data on individual fishing
portfolios, this type of model allows certain strategies and levels of
diversification to be more or less variable than others.

We extended the basic variance function regression to a hierarchical
Bayesian variance function regression model with Gaussian errors
predicting $\log$ revenue, $\log(R_{i,t})$, for
each fisher $i$ and time $t$:

@@

We fit our models with Stan 2.11.1
[@hoffman2014; @standevelopmentteam2015; @standevelopmentteam2015a; @carpenter2015]
and R 3.3.1 [@rcoreteam2016].
Stan implements the
No-U-Turn Hamiltonian Markov chain Monte Carlo algorithm [@hoffman2014]
to perform Bayesian statistical inference.
We assigned weakly informative priors on all parameters:
$N(0, 2^2)$ priors on all
$\beta$, $\gamma$, and $\eta$ parameters,
and half-$t(3, 0, 2)$ priors
(i.e. degrees of freedom of 3 and scale of 2)
on all $\sigma$ parameters.
We ran four chains and 2,000 iterations and discarded
the first 1,000 iterations of each chain
as warm up (i.e. 4,000 final samples).
We checked for chain convergence visually with trace plots.
We also ensured that $\hat{R}<1.05$ (the potential scale reduction factor)
and that the effective sample size,
as calculated by the rstan package,
was greater than 200 for all parameters [@gelman2014].
We verified that our model returned sensible estimates by
comparing our estimates to an ad-hoc two-stage
model fit with the lme4 R package [@bates2015],
and by fitting our model to simulated data
and recovering the true values (Supporting Information).
Code to reproduce our results (with a simulated data set)
is available at <https://github.com/NCEAS/pfx-commercial>.

>>>>

We combined similar permits into permit groupings
and identified sets of
permit groupings held by an individual
in a specific year as 'strategies' (Supporting Information).
For example, we combined permits that were the same except for vessel size
(e.g. a longliner fishing sablefish on a vessel under 60 ft was
considered to have the same strategy as a longliner fishing
sablefish on a vessel over 60 ft),
and we combined a number of permits that were targeting a single species
and differed only in region fished.
Therefore, someone fishing herring roe in Kodiak
and someone fishing herring roe in Alaska Peninsula
were both considered to have a 'herring roe' permit group.
For salmon permits,
we grouped permits using the same gear type across regions
for groups that shared similar species composition.
After this process of combining permits,
we were left with `r n_grouped_permits`
unique fishing permit groups (Table S\ref{tab:strategies}),
which we aggregated
within each person-year combination
to form permit strategies.
For example, if someone fished halibut
and sablefish in the same year,
their strategy for that year would be "halibut-sablefish".
Specific details on our strategy definitions are available in
the Supporting Information.

@@

\noindent
where $s$ indexes species from $1$ through $n$.
We calculated effort or effective season length as
the sum of the season lengths for each permit each year.
Season length for a given permit
was calculated as the number of days between
the first instance of fishing a permit
and the last instance of fishing a permit each year.
For example, if someone fished for 30 days
on a salmon drift gillnet permit in Southeast Alaska
and 40 days on a statewide longline halibut permit,
that individual's season length
would be 70 days.

@@

To jointly model revenue and revenue variability as a function of
individual-level covariates, we use a variance function regression model, which
separately models change in the mean and variance as
a function of covariates [e.g. @davidian1987; @hall1989]. 
Whereas traditional linear models or 
hierarchical linear models generally assume
homoscedasticity --- that the residual variance 
is the same for all values of the predictor variables ---
the variance-function regression model allows the variance to be heteroscedastic. 
For application to economic data on individual fishing
portfolios, this type of model allows certain strategies and levels of
diversification to be more or less variable than others.

We extended the basic variance-function regression to a hierarchical
Bayesian variance-function regression model with Gaussian errors
predicting $\log$ revenue, $\log(R_{i,t})$, for
each fisher $i$ and time $t$:

@@

We fit our models with Stan 2.11.1
[@hoffman2014; @standevelopmentteam2015; @standevelopmentteam2015a; @carpenter2015]
and R 3.3.1 [@rcoreteam2016].
Stan implements the
No-U-Turn Hamiltonian Markov chain Monte Carlo algorithm [@hoffman2014]
to perform Bayesian statistical inference.
We assigned weakly informative priors on all parameters:
$N(0, 2^2)$ priors on all
$\beta$, $\gamma$, and $\eta$ parameters,
and half-$t(3, 0, 2)$ priors
(i.e. degrees of freedom of 3 and scale of 2)
on all $\sigma$ parameters to allow for heavier tails.
We ran four chains and 2,000 iterations and discarded
the first 1,000 iterations of each chain
as warm up (i.e. 4,000 final samples).
We checked for chain convergence visually with trace plots.
We also ensured that $\hat{R}<1.05$ (the potential scale reduction factor)
and that the effective sample size,
as calculated by the rstan R package [@standevelopmentteam2015],
was greater than 200 for all parameters [@gelman2014].
We verified that our model returned sensible estimates by
comparing our estimates to an ad-hoc two-stage
model fit with the lme4 R package [@bates2015],
and by fitting our model to simulated data
and recovering the true values (Supporting Information).
Code to reproduce our results (with a simulated data set)
is available at <https://github.com/NCEAS/pfx-commercial>.
